---
title: "Group Lab 1"
author: "Group 1"
date: "January 16, 2019"
output: html_document
---

```{r setup, warning=FALSE, echo=FALSE, message=FALSE}
library(tidyverse)
library(knitr)
library(stringr)

object1=read.csv("China_EO_49to17.csv")
object2=as_tibble(object1)
```


# Part 2: Looking at the data

A couple of interesting things can be gleaned from the data. One is the fact that China is not entirely comprised of provinces.
There are 4 cities within the dataset that comprise China's municipalities: Beijin, Tianjin, Shanghai, Chongqing. These municipalities 
both hold the rank of both city and provinces themselves. As a result, they hold some of the highest growth. Take a look at these four
cities industrial output side-by side

(Put map here)

Enterprises are companies or production units
Ouput are in RMB which represent the provinces' GDP

```{r echo=FALSE, message=FALSE}
province_name <- "Beijing_Enterprise"
columnNames <- colnames(object2)
enterprises <- columnNames[grep("Enterprise", columnNames)]
outputs <- columnNames[grep("Output", columnNames)]
p <- ggplot(data = object2, aes(Year))
for(i in 1:15){
  p <- p + geom_line(aes_string(y = enterprises[i], color=shQuote(enterprises[i])), size = 1)
}
p


q <- ggplot(data = object2, aes(Year))
for(i in 1:10){
  q <- q + geom_line(aes_string(y = outputs[i], color=shQuote(outputs[i])), size = 1)
}
q

```

