---
title: "Group Lab 1"
author: "Group 1"
date: "January 16, 2019"
output: html_document
---

```{r setup, warning=FALSE, echo=FALSE}
library(tidyverse)
library(reshape2)
object1=read.csv("China_EO_49to17.csv")
object2=as_tibble(object1)

majorCities <- select(object2, Beijing_Output, Shanghai_Output, Tianjin_Output, Chongqing_Output, Year) 

majorCities <- melt(majorCities, id="Year")
part2map1 <-ggplot(data=majorCities,aes(x=Year, y=value, color=variable)) + geom_line()
                                     
```


# Part 2: Looking at the data

A couple of interesting things can be gleaned from the data. One is the ffact that China is not entirely comprised of provinces. There are 4 cities within the dataset that comprise China's municipalities: Beijing, Tianjin, Shanghai, Chongqing. These municipalities both hold the rank of both city and provinces themselves. As a result, they hold some of the highest growth. Take a look at these four cities industrial output side-by side


```{r, echo=FALSE}
part2map1
```  

As you can see, the rate of growth is massive starting around 1990. One thing that stands out is that Shanghai started growing a lot earlier than the other municipalities. If we take a further look at this...

r is hard 