---
title: "Group Lab 1"
author: "Group 1"
date: "January 16, 2019"
output: html_document
---

```{r setup, warning=FALSE, echo=FALSE, include=FALSE}
library(tidyverse)
library(reshape2)
library(ggplot2)
library(knitr)
library(RColorBrewer)

object1=read.csv("China_EO_49to17.csv")
object2=as_tibble(object1)
                                     
```

# Part 2: Looking at the data

A couple of interesting things can be gleaned from the data. One is the fact that China is not entirely comprised of provinces.
There are 4 cities within the dataset that comprise China's municipalities: Beijin, Tianjin, Shanghai, Chongqing. These municipalities 
both hold the rank of both city and provinces themselves. As a result, they hold some of the highest growth. Take a look at these four
cities industrial output side-by side


```{r echo=FALSE, message=FALSE, warning=FALSE}
majorCities <- select(object2, Beijing_Output, Shanghai_Output, Tianjin_Output, Chongqing_Output, Year) 
majorCities <- melt(majorCities, id="Year")
part2map1 <-ggplot(data=majorCities,aes(x=Year, y=value, color=variable)) + geom_line()
part2map1
```  

As you can see, the rate of growth is massive starting around 1990. This is consistent with the rise of manufacturing in China and also the easing of regulations for private businesses. One thing that stands out is that Shanghai started growing a lot earlier than the other municipalities, which may stem to its location as a port city.

How does this compare to the output of the provinces of places like Tibet or Inner Mongolia, considered autonomous regions because they have a majority-minority population. Let's take a look at their output for the 5 provinces. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
autonomousRegions <- select(object2, Xinjiang_Output, Ningxia_Output, Tibet_Output, Guangxi_Output, InnerMongolia_Output, Year)
autonomousRegions <- melt(autonomousRegions, id="Year")
part2map2 <- ggplot(data=autonomousRegions, aes(x=Year, y=value, color=variable)) + geom_line()
part2map2
```

While there are a lot of missing values, the most notable thing is that aside from 

if you're noticing that the dataset has a lot of missing values, you are correct! Since our dataset was sourced from a private source, some of the values are missing. It could be that missing values are more prevelant for smaller provinces? How can we figure this out? With R, of course. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
columnNames <- colnames(object2)  #get column names and store in vector
enterprises <- columnNames[grep("Enterprise", columnNames)]  #subset the data to only get the enterprise names
province_names <- gsub("_.*$","", enterprises) #trim the vector to get only the province names
outputs <- columnNames[grep("Output", columnNames)] #subset the data to only get the output names


data2017 <-subset(object2, Year == "2017")  #subset data for the 2017 year
data2017 <- data2017[,enterprises]          #get only the enterprise data
data2017 <- as.numeric(data2017[1,])      #store the vector as numeric vector
df2017 <- data.frame(province_names,data2017) #create data from with province names and enterprise data 
colourCount = length(unique(df2017$province_names))  #get number of unique colors to ramp color set
getPalette = colorRampPalette(brewer.pal(3, "Set1")) #create a palette 


enterprises_bar <- ggplot(df2017, aes(y = data2017,x= province_names, fill = province_names)) + #create plot
  geom_bar(stat ="identity") +                                                                  
  scale_fill_manual(values = getPalette(colourCount)) +   #give bars unique colors                      
  theme(axis.text.x=element_text(angle=-45, vjust=0.5, hjust=0), legend.position="none") +   #angle province
  labs(title="Number of Enterprises in China 2017",               #title for x,y, and main
                x ="Provinces/Municipalities", y = "Amount of Enterprises")


data2011_enterprise <-subset(object2, Year == "2011")  #subset data for 2011 year
data2011_enterprise <- data2011_enterprise[,enterprises]   #get only enterprise data
data2011_enterprise <- as.numeric(data2011_enterprise[1,])  #store the vector as numeric vector
df2011_enterprise <- data.frame(province_names,data2011_enterprise)  #create data from with names and data
colourCount = length(unique(df2011_enterprise$province_names)) #get number of unique colors to ramp color set
getPalette = colorRampPalette(brewer.pal(3, "Set1"))  #create color paletee

enterprises_bar2011 <- ggplot(df2011_enterprise, aes(y = data2011_enterprise,x= province_names, fill = province_names)) +  #plot 
  geom_bar(stat ="identity") + 
  scale_fill_manual(values = getPalette(colourCount)) + #get unique colors to bars
  theme(axis.text.x=element_text(angle=-45, vjust=0.5, hjust=0), legend.position="none") + 
  labs(title="Number of Enterprises in China 2011", #title
       x ="Provinces/Municipalities", y = "Amount of Enterprises")

data2011_output <-subset(object2, Year == "2011")  #subset data for 2011
data2011_output <- data2011_output[,outputs]   #get only the output data
data2011_output <- as.numeric(data2011_output[1,])  #store the vector as numeric vector
df2011_output <- data.frame(province_names,data2011_output) #create data frame from names and output
colourCount2 = length(unique(df2011_output$province_names)) #get number of unique colors to ramp color set
getPalette2 = colorRampPalette(brewer.pal(3, "Set1"))  #create color palette
output_bar <- ggplot(df2011_output, aes(y = data2011_output,x= province_names, fill = province_names)) + #plot
  geom_bar(stat ="identity") + 
  scale_fill_manual(values = getPalette(colourCount)) + #give color to bars
  theme(axis.text.x=element_text(angle=-45, vjust=0.5, hjust=0), legend.position="none") + #angle names 
  labs(title="GDP in China 2011", #title 
     x ="Provinces/Municipalities", y = "GDP (RMB)")
```
```{r  echo=FALSE, message=FALSE, warning=FALSE}
# print out number of Enterprises in 2017
enterprises_bar
```

This graph shows the number of enterprises or conglomerates in each province/municipalities in 2017. According to the graph, Guangdong, Jiangsu, Shandong, and Zhejiang are the top provinces which hold the most enterprises in 2017. Which coincides with the idea that these provinces do the most sales in the country. The reason why I was interested in viewing the number of enterprises in each province because it is easier to see which province may be doing the most business and which provinces are doing less business and has less business activity. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
#print out number of Enterprises in 2011
enterprises_bar2011
```

This graph shows the number of enterprises in each province in 2011. The reason why I chose 2011 is because when I was looking for the GDP for each province in the most recent years, there were a lot of data missing. To my discretion, I chose 2011 as there were a good amount of data in both the number of enterprises in each province, as well as providing the GDP for each province. By having the same year for both data, it is much easier to compare the two variables. In 2011,  the same provinces hold most of the enterprises Guangdong, Jiangsu, Shandong, and Zhejiang. Let's see if the same provinces have the highest GDP of China.

```{r echo=FALSE, message=FALSE, warning=FALSE}
#print out GDP in 2011
output_bar
```

Looking at the GDP in China 2011, we see that the same 4 provinces also have the greatest GDP In China. The only thing that is interesting is that even though Zhejiang has similar amount of enterprises as Shandong, Zhejiang has a lower GDP rate. 



